---
title: "forester tutorial for AutoML classes"
author: "Hubert Ruczyński"
output: html_notebook
---

# forester tutorial for AutoML classes

[Repository](https://github.com/ModelOriented/forester)

## Installation

```{r message=FALSE}
install.packages("devtools")
devtools::install_github("ModelOriented/forester")
devtools::install_url('https://github.com/catboost/catboost/releases/download/v1.1.1/catboost-R-Darwin-1.1.1.tgz', INSTALL_opts = c("--no-multiarch", "--no-test-load", "--no-staged-install"))
devtools::install_github('catboost/catboost', subdir = 'catboost/R-package')
devtools::install_github('ricardo-bion/ggradar', dependencies = TRUE)
install.packages('tinytex')
tinytex::install_tinytex()
```

## Imports

```{r}
library(forester)
```

## Task 1: Importing dataset

Find a tabular dataset on the internet for regression or binary classification task, and import it to the notebook with the following function.

```{r}
df <- read.csv(file = 'FILE_NAME', header = TRUE, sep = ',')
```

## Task 2: Data check

Use the forester's function for checking you datasets quality. Analyse the results, and write down what issues does it have.

```{r}
?check_data
```

Answer/Analysis:

## Task 3: Custom preprocessing

Use the forester's custom preprocessing function to fix the data issues detected in the previous task, and run the data check again to verify if it worked properly.

```{r}
?custom_preprocessing
```

## Task 4: Model training

Use the main train function to train the baseline models.

**TIP** If you want to obtain the results faster, limit the number of iterations for Bayesian Optimization.

```{r}
?train
```

## Task 5: Explore the function output

Explore what information does the output of train() function contain. Particularly, answer the following questions:

1.  What are the indexes of outliers?
2.  What are the engines for best 5 models on validation dataset?
3.  Can we access the data used for training, testing , and validation? How?
4.  Can we access the prediction for training, testing , and validation datasets? How?
5.  Which models obtained the best scores for each of training, testing , and validation datasets?
6.  Provide the comparison of top 5 models with all calculated metrics.

**TIP** In R, you can use `head()` to print first rows of the dataframe

```{r}

```

## Task 6: Training report

With the usage of `report()` function, generate an Automatic report for our training task, and explore insights about obtained results.

```{r}
?report
```

## Task 7: Try to improve

Read the documentation of train, and custom preprocessing again, and try to design you AutoML framework better, so you achieve the results with higher quality.

```{r}

```
